Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
conc

We have presented two approaches to synthesize state feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the system's dynamics 
up to the completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
Both approaches are novel in the control system literature in that it puts
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering the various error sources in the implementation 
of the control algorithm and in the computational modeling of plant dynamics.
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  In particular, both approaches
complement each other and together solve all benchmarks provided in the set.
Future work will be the extension of these approaches to consider performance 
requirements while synthesizing digital controllers.

>>>>

We have presented two approaches to synthesize state feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the system's dynamics 
up to the completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
Both approaches are novel in the control system literature in that it puts
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering the various error sources in the implementation 
of the control algorithm and in the computational modeling of plant dynamics.
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  In particular, both approaches
complement each other and together solve all benchmarks provided in the set.
Future work will be the extension of these approaches to consider performance 
requirements while synthesizing digital controllers and the application of them
for synthesizing state observers that generally appears in state feedback 
architecture.
